One more attempt on ArXe

### 2016-01-27 structures.tex
change characterization in table 2

In a gas expansion a range of clusters sizes with different structures is produced. 
However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had a (slightly) enhanced abundance over other sizes. 
We therefore started from icosahedral structures and produced mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms to a given structure close to the desired position. 
After that, the cluster structures were optimized using the UFF force field method \cite{} implemented in the 
Avogadro programme \cite{}.
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_2_overview.pdf}
 \caption{Cluster structures composed of 13 argon atoms and two additional xenon
          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
          (a) closest possible, (b) middle, (c) furthest away.}
 \label{figure:cluster_2_overview}
\end{figure}
%
\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_3_overview.pdf}
 \caption{Cluster structures derived from a 55 atom icosahedral structure:
          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
          grouped on one side, (c) six xenon atoms distributed randomly
          in a 55 atoms cluster.}
 \label{figure:cluster_3_overview}
\end{figure}

>>>>

In a gas expansion a range of clusters sizes with different structures is produced. 
However, for small rare gas clusters consisting of less than approximately \unit[1000]{atoms} so-called \emph{islands of stability} were found.\cite{haberland}  
In mass spectra, clusters with mass numbers corresponding to icosahedral shapes had a (slightly) enhanced abundance over other sizes. 
We therefore started from icosahedral structures and produced mixed cluster structures by substitution of individual atoms with one or the other kind (Ar or Xe), or added individual atoms to a given structure close to the desired position. 
After that, the cluster structures were optimized using the UFF force field method \cite{} implemented in the 
Avogadro programme \cite{}.
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_2_overview.pdf}
 \caption{Cluster structures composed of 13 argon atoms and two additional xenon
          atoms on different surfaces of the argon icosahedron, varying in Xe-Xe distance:
          (a) closest possible, (b) middle, (c) furthest away. They refer to
          numbers 8--10 in Table \ref{table:theo_gammas}.}
 \label{figure:cluster_2_overview}
\end{figure}
%
\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/cluster_3_overview.pdf}
 \caption{Cluster structures derived from a 55 atom icosahedral structure:
          (a) one xenon atom on the surface, (b) six xenon atoms inside a 55 atoms cluster,
          grouped on one side, (c) six xenon atoms distributed randomly
          in a 55 atoms cluster. They refer to numbers 11, 17 and 18
          in Table \ref{table:theo_gammas}.}
 \label{figure:cluster_3_overview}
\end{figure}

### 2016-01-27 theo_results.tex
change characterization in table 2

\begin{table*}[th]

@@

\caption{Calculated properties of some model clusters. Columns `ICD' and `ETMD'

@@

\begin{tabular}{lrrrccr}

@@

name                 & Xe atoms & Ar atoms & Xe$_{\rm cl}$ \% & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\

@@

ArXe\_2\_1atom       &      1   &     12   &  7.7  & 0.000 & 0.000 &  --\\ %    0.0            \\
ArXe\_3\_1atom       &      1   &     54   &  1.8  & 0.000 & 0.000 &  --\\ %    0.0            \\ 
ArXe\_3\_2atom       &      2   &     53   &  3.6  & 0.033 & 0.167 &  16.7\\ %2.006$\cdot 10^{-5}$ \\
ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039 & 2.573 &  73.2\\ %9.612$\cdot 10^{-4}$ \\

@@

XeAr\_2\_surface     &      1   &     13   &  7.1  & 0.792 & 0.000 & 100.0\\ %7.922$\cdot 10^{-5}$ \\
XeAr\_2\_edge        &      1   &     13   &  7.1  & 0.013 & 0.000 & 100.0\\ %1.320$\cdot 10^{-6}$ \\
XeAr\_2\_vertex      &      1   &     13   &  7.1  & 0.050 & 0.000 & 100.0\\ %5.013$\cdot 10^{-6}$ \\
XeAr\_2\_2top        &      2   &     13   & 13.3  & 0.101 & 0.151 &  40.1\\ %2.523$\cdot 10^{-5}$ \\
XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 0.159 & 0.008 &  95.4\\ %1.665$\cdot 10^{-5}$ \\
XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 0.159 & 0.002 &  98.9\\ %1.605$\cdot 10^{-5}$ \\
XeAr\_3\_surface     &      1   &     55   &  1.8  & 0.064 & 0.000 & 100.0\\ %6.371$\cdot 10^{-6}$ \\
XeAr\_3\_edge        &      1   &     55   &  1.8  & 0.048 & 0.000 & 100.0\\ %4.791$\cdot 10^{-6}$ \\
XeAr\_3\_vertex      &      1   &     55   &  1.8  & 0.027 & 0.000 & 100.0\\ %2.701$\cdot 10^{-6}$ \\
XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 0.077 & 0.000 & 100.0\\ %7.708$\cdot 10^{-6}$ \\
XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 0.053 & 0.000 & 100.0\\ %5.258$\cdot 10^{-6}$ \\
XeAr\_3\_2in         &      2   &     53   &  3.6  & 0.117 & 0.055 &  68.1\\ %1.711$\cdot 10^{-5}$ \\
XeAr\_3\_6in         &      6   &     49   & 10.9  & 0.375 & 0.405 &  48.1\\ %7.796$\cdot 10^{-5}$ \\
XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 0.292 & 0.674 &  30.3\\ %9.660$\cdot 10^{-5}$ \\

@@

\end{table*}

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/2tops.pdf}
 \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
          argon clusters consisting of 13
          argon atoms with two additional xenon atoms on top of two different
          argon surfaces. ICD and ETMD spectra are shown for three
          different relative positions of the two xenon atoms. If 
          the xenon atoms are close to each other, an ETMD process is
          clearly visible. In the other two cases the spectra are dominated by
          the ICD spectrum.
          {\it Q: Ich sehe die traces für die 'furthest' Konfiguration nicht(?!) Q: Warum ist in diesen (und vielen anderen) Bildern jedes Label doppelt?}}
 \label{figure:2tops}
\end{figure}
%
For clusters with more than one xenon atom, also ETMD(3) is possible.
Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
spectra do not change qualitatively by adding the second xenon.
%either identical or at least very similar to the ones for
%cluster with a single  consisting of one
%convoluted peak at approximately \unit[0.2]{eV}. 
However, the ETMD(3) spectra
are very sensitive to the relative position of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peaks due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
between the electron transfer unit and the xenon atom ionized in the final state.
The larger the distance between the xenon atoms, the higher are the energies
of the secondary electrons and the smaller are the decay widths. 
Therefore, a
significant contribution from ETMD(3) compared to ICD is only
seen if the two xenon atoms reside on two adjacent
surfaces. 
%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see \ref{sec:exp_results}).
%
%The threefold peak structure of the ETMD(3) peak does in contrast to
%the ICD spectrum not stem from different triple structures but from the
%four different decay channels for one triple structure.

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/xe_8_1lay.pdf}
 \caption{Same as Figure \protect\ref{figure:2tops}, for a large cluster consisting
          of a xenon core of 1415 atoms surrounded by one complete layer of
          argon atoms. {\it Q: War: `two complete layers' - bitte \"uberpr\"ufen.} The ICD and ETMD peak overlap such, that the peak structure
          might not be visible.}
 \label{figure:xe_8_lay1}
\end{figure}
%
In the first experiments very large argon-xenon clusters were measured,\cite{Mucke_phd}
which we approximate by a cluster consisting of 1415 xenon atoms surrounded
by one layer of argon atoms. The spectra are shown in Figure
\ref{figure:xe_8_lay1}.

>>>>

\begin{table}[h]
\small

@@

\caption{Structural and calculated properties of some model clusters.
The cluster structures are characterized by the number of
Ar and Xe atoms in the cluster. The first group has a xenon core
surrounded by argon atoms while the second group except for
number 18 has a xenon core. The last group of structures was taken
from Reference \cite{} and contains various structures.
The structures are then categorized (str. cl.) into core-layer (cl)
structures, structures, where single atoms in the outermost layer
are replaced by the different atom type (in) and mixed structures, that
do not show a clear layer structure. In case one atom is placed on top
of a cluster or replaces a different atom in the outermost layer, its
position is given as surface/edge/vertex. In case two atoms are placed
on top of a cluster, their relative position is declared.
The columns `ICD' and `ETMD'

@@

\begin{tabular}{rrrrcccccr}

@@

\# & \# Xe & \# Ar & Xe$_{\rm cl}$\% & str. cl. & pos. & rel. pos. & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\

@@

 1 &     1 &    12 &  7.7  & cl    &         &          & 0.000 & 0.000 &  --\\ %    0.0            \\     ArXe\_2\_1atom      
 2 &     1 &    54 &  1.8  & cl    &         &          & 0.000 & 0.000 &  --\\ %    0.0            \\     ArXe\_3\_1atom      
 3 &     2 &    53 &  3.6  & cl    &         &          & 0.033 & 0.167 &  16.7\\ %2.006$\cdot 10^{-5}$ \\ ArXe\_3\_2atom      
 4 &  1415 &   642 & 68.8  & cl    &         &          & 7.039 & 2.573 &  73.2\\ %9.612$\cdot 10^{-4}$ \\ ArXe\_8\_1layer     

@@

 5 &     1 &    13 &  7.1  & cl    & surface &          & 0.792 & 0.000 & 100.0\\ %7.922$\cdot 10^{-5}$ \\ XeAr\_2\_surface    
 6 &     1 &    13 &  7.1  & cl    & edge    &          & 0.013 & 0.000 & 100.0\\ %1.320$\cdot 10^{-6}$ \\ XeAr\_2\_edge       
 7 &     1 &    13 &  7.1  & cl    & vertex  &          & 0.050 & 0.000 & 100.0\\ %5.013$\cdot 10^{-6}$ \\ XeAr\_2\_vertex     
 8 &     2 &    13 & 13.3  & cl    &         & closest  & 0.101 & 0.151 &  40.1\\ %2.523$\cdot 10^{-5}$ \\ XeAr\_2\_2top       
 9 &     2 &    13 & 13.3  & cl    &         & middle   & 0.159 & 0.008 &  95.4\\ %1.665$\cdot 10^{-5}$ \\ XeAr\_2\_2midtop    
10 &     2 &    13 & 13.3  & cl    &         & furthest & 0.159 & 0.002 &  98.9\\ %1.605$\cdot 10^{-5}$ \\ XeAr\_2\_2endtop    
11 &     1 &    55 &  1.8  & cl    & surface &          & 0.064 & 0.000 & 100.0\\ %6.371$\cdot 10^{-6}$ \\ XeAr\_3\_surface    
12 &     1 &    55 &  1.8  & cl    & edge    &          & 0.048 & 0.000 & 100.0\\ %4.791$\cdot 10^{-6}$ \\ XeAr\_3\_edge       
13 &     1 &    55 &  1.8  & cl    & vertex  &          & 0.027 & 0.000 & 100.0\\ %2.701$\cdot 10^{-6}$ \\ XeAr\_3\_vertex     
14 &     1 &    54 &  1.8  & in    & edge    &          & 0.077 & 0.000 & 100.0\\ %7.708$\cdot 10^{-6}$ \\ XeAr\_3\_edge\_in   
15 &     1 &    54 &  1.8  & in    & vertex  &          & 0.053 & 0.000 & 100.0\\ %5.258$\cdot 10^{-6}$ \\ XeAr\_3\_vertex\_in 
16 &     2 &    53 &  3.6  & in    &         &          & 0.117 & 0.055 &  68.1\\ %1.711$\cdot 10^{-5}$ \\ XeAr\_3\_2in        
17 &     6 &    49 & 10.9  & in    &         &          & 0.375 & 0.405 &  48.1\\ %7.796$\cdot 10^{-5}$ \\ XeAr\_3\_6in        
18 &     6 &    49 & 10.9  & mixed &         &          & 0.292 & 0.674 &  30.3\\ %9.660$\cdot 10^{-5}$ \\ XeAr\_3\_6\_scat    
19 &     2 &    36 &  5.3  & cl    &         &          & 0.117 & 0.151 &  43.6\\                        % Ar$_{36}$Xe$_{2}$   
20 &     4 &    34 & 10.5  & mixed &         &          & 0.248 & 0.587 &  29.7\\                        % Ar$_{34}$Xe$_{4}$   
21 &     5 &    33 & 13.2  & mixed &         &          & 0.335 & 0.844 &  28.4\\                        % Ar$_{33}$Xe$_{5}$   
22 &    13 &    25 & 34.2  & mixed &         &          & 0.828 & 5.414 &  13.3\\                        % Ar$_{25}$Xe$_{13}$  
23 &    24 &    14 & 63.2  & mixed &         &          & 1.488 &16.718 &   8.2\\                        % Ar$_{14}$Xe$_{24}$  
24 &    25 &    13 & 65.8  & in    &         &          & 1.432 & 4.995 &  22.3\\                        % Ar$_{13}$Xe$_{25}$  
25 &    35 &     3 & 92.1  & in    &         &          & 2.017 & 7.051 &  22.2\\                        % Ar$_{3}$Xe$_{35}$   

@@

\end{table}

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/2tops.pdf}
 \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
          argon clusters consisting of 13
          argon atoms with two additional xenon atoms on top of two different
          argon surfaces. ICD and ETMD spectra are shown for three
          different relative positions of the two xenon atoms. If 
          the xenon atoms are close to each other, an ETMD process is
          clearly visible. In the other two cases the spectra are dominated by
          the ICD spectrum.}
 \label{figure:2tops}
\end{figure}
%
For clusters with more than one xenon atom, also ETMD(3) is possible.
Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
spectra do not change qualitatively by adding the second xenon.
%either identical or at least very similar to the ones for
%cluster with a single  consisting of one
%convoluted peak at approximately \unit[0.2]{eV}. 
However, the ETMD(3) spectra
are very sensitive to the relative position of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peaks due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
between the electron transfer unit and the xenon atom ionized in the final state.
The larger the distance between the xenon atoms, the higher are the energies
of the secondary electrons and the smaller are the decay widths. 
Therefore, a
significant contribution from ETMD(3) compared to ICD is only
seen if the two xenon atoms reside on two adjacent
surfaces. 
%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see \ref{sec:exp_results}).
%
%The threefold peak structure of the ETMD(3) peak does in contrast to
%the ICD spectrum not stem from different triple structures but from the
%four different decay channels for one triple structure.

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/xe_8_1lay.pdf}
 \caption{Same as Figure \protect\ref{figure:2tops}, for a large cluster consisting
          of a xenon core of 1415 atoms surrounded by one complete layer of
          argon atoms. The ICD and ETMD peak overlap such, that the peak
          structure might not be visible.}
 \label{figure:xe_8_lay1}
\end{figure}
%
In the first experiments very large argon-xenon clusters were measured,\cite{Mucke_phd}
which we approximate by a cluster consisting of 1415 xenon atoms surrounded
by one layer of argon atoms. The spectra are shown in Figure
\ref{figure:xe_8_lay1}.
